RJObject Paper

### 2014-06-23 Documents/Paper/ms.tex
Wording change

The Metropolis acceptance probability must include the following factor:
\begin{eqnarray}
\frac{\prod_{i=1}^N p(x_i | \alpha')}{\prod_{i=1}^N p(x_i | \alpha)}
\end{eqnarray}

Since this proposal leaves the objects $\{x_i\}$ fixed, it will usually not
affect the value of the likelihood, and therefore the likelihood will not need
to be recomputed.

>>>>

The overall Metropolis acceptance probability
for this kind of move, if sampling the prior (or the constrained prior of DNS)
must include the following factor:
\begin{eqnarray}
\frac{\prod_{i=1}^N p(x_i | \alpha')}{\prod_{i=1}^N p(x_i | \alpha)}
\end{eqnarray}
Since this proposal leaves the objects $\{x_i\}$ fixed, it will usually not
affect the value of the likelihood, and therefore the likelihood will not need
to be recomputed.
